### 2013-11-14 Rcode/conservativepm.Rmd
updated figures and text

    betahat.qval[[i]] = qvalue(pval[[i]])
    betahat.fdrtool[[i]] = fdrtool(pval[[i]],statistic="pvalue",plot=FALSE)
    betahat.locfdr[[i]] = locfdr(zscore[[i]],nulltype=0,plot=0)
    betahat.mixfdr[[i]] = mixFdr(zscore[[i]],noiseSD=1,theonull=TRUE,plot=FALSE)
  }
  return(list(beta =beta,
  betahatsd=betahatsd,
  betahat = betahat,
  zscore = zscore,
  pval = pval,
  betahat.ash.n = betahat.ash.n,
  betahat.ash.u = betahat.ash.u,
  betahat.ash.npm = betahat.ash.npm,
  betahat.ash.true=betahat.ash.true,
  betahat.qval = betahat.qval,
  betahat.fdrtool = betahat.fdrtool,
  betahat.locfdr = betahat.locfdr,
  betahat.mixfdr = betahat.mixfdr,
    pi0=pi0))
}    
```

@@

simres1 = basicsim(mixsd,mixpi_alt,niter=200,nsamp=1000)
simres1a = basicsim(mixsd,mixpi_alt,niter=200,nsamp=10000)
simres2= basicsim(c(0,4),c(1))
simres3=basicsim(c(0,4),c(1),bsd=c(rep(1,500),rep(10,500)))
simres4=basicsim(c(0,4),c(1),bsd=c(rep(1,500),rep(10,500)),minpi0=0.9,seed=200)
```

@@

  plot_pi0 = function(sims){
    pi0=sims$pi0  
    pi0_ash.n=unlist(lapply(sims$betahat.ash.n,get_pi0))
    pi0_ash.u=unlist(lapply(sims$betahat.ash.u,get_pi0)) 
    pi0_fdrtool = unlist(lapply(sims$betahat.fdrtool,get_pi0.fdrtool))
    pi0_locfdr=unlist(lapply(sims$betahat.locfdr,get_pi0.locfdr))
    pi0_mixfdr = unlist(lapply(sims$betahat.mixfdr,get_pi0.mixfdr))
    pi0_qval = unlist(lapply(sims$betahat.qval,"[[","pi0"))

    res = data.frame(pi0=pi0,qvalue=pi0_qval,mixfdr=pi0_mixfdr, locfdr=pi0_locfdr, fdrtool=pi0_fdrtool,ash.nullbiased=pi0_ash.n,ash.uniform=pi0_ash.u)
    require(reshape2)
    res.melt = melt(res, id.vars=c("pi0"),variable.name="Method")
    p=ggplot(data=res.melt,aes(pi0,value,colour=Method)) +geom_point(shape=16) +
        geom_abline(colour = "black") +
        xlab("True pi0") +
        ylab("Estimated pi0")
    print(p +scale_y_continuous(limits=c(0,1)) +
          scale_x_continuous(limits=c(0,1)) +
          coord_equal(ratio=1))

@@

  pdf("figures/estpi0_sim1.pdf")
    plot_pi0(simres1)
  dev.off()
  pdf("figures/estpi0_sim2.pdf")
    plot_pi0(simres2)
  dev.off()

@@

```{r}
mean_quant=function (x, mult = 1){
      x <- na.omit(x)
      sd <- mult * sqrt(var(x))
      mean <- mean(x)
      data.frame(y = median(x), ymin = quantile(x,0.25) , ymax = quantile(x,0.75))
}

@@

    cbbPalette <- c("#000000","#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
    labels = c('ash (null-biased)','ash (uniform)')
    breaks = c("ash.nullbiased","ash.uniform")
    if(ptype=="lfdr"){
      labels = c('mixfdr', labels)
      breaks = c("mixfdr", breaks)
    }

@@

    res.melt = melt(res, id.vars=c("Bayes","Scenario","Measure"),variable.name="Method")

    cbbPalette <- c("#000000","#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
    labels = c('mixfdr','ash (null-biased)','ash (uniform)')
    breaks = c("mixfdr","ash.nullbiased","ash.uniform")

@@

>>>>

    cat("applying q value\n")
    betahat.qval[[i]] = qvalue(pval[[i]])
    cat("applying fdrtool\n")
    betahat.fdrtool[[i]] = fdrtool(pval[[i]],statistic="pvalue",plot=FALSE)
    cat("applying locfdr\n")
    betahat.locfdr[[i]] = try(locfdr(zscore[[i]],nulltype=0,plot=0))
    cat("applying mixfdr\n")
    betahat.mixfdr[[i]] = mixFdr(zscore[[i]],noiseSD=1,theonull=TRUE,plot=FALSE)
  }
  return(list(beta =beta,
  betahatsd=betahatsd,
  betahat = betahat,
  zscore = zscore,
  pval = pval,
  betahat.ash.n = betahat.ash.n,
  betahat.ash.u = betahat.ash.u,
  betahat.ash.npm = betahat.ash.npm,
  betahat.ash.true=betahat.ash.true,
  betahat.qval = betahat.qval,
  betahat.fdrtool = betahat.fdrtool,
  betahat.locfdr = betahat.locfdr,
  betahat.mixfdr = betahat.mixfdr,
    pi0=pi0))
}    
```

@@

simres1 = basicsim(mixsd,mixpi_alt,niter=200,nsamp=1000)
simres1a = basicsim(mixsd,mixpi_alt,niter=200,nsamp=10000)
simres2= basicsim(c(0,4),c(1))
simres3=basicsim(c(0,2),c(1),bsd=c(rep(1,500),rep(10,500)))
simres4=basicsim(c(0,2),c(1),bsd=c(rep(1,500),rep(10,500)),minpi0=0.9,seed=200)
```

@@

  plot_pi0 = function(sims){
    res=list()
    for(i in 1:length(sims)){
      pi0=sims[[i]]$pi0  
      pi0_ash.n=unlist(lapply(sims[[i]]$betahat.ash.n,get_pi0))
      pi0_ash.u=unlist(lapply(sims[[i]]$betahat.ash.u,get_pi0)) 
      pi0_fdrtool = unlist(lapply(sims[[i]]$betahat.fdrtool,get_pi0.fdrtool))
      pi0_locfdr=unlist(lapply(sims[[i]]$betahat.locfdr,get_pi0.locfdr))
      pi0_mixfdr = unlist(lapply(sims[[i]]$betahat.mixfdr,get_pi0.mixfdr))
      pi0_qval = unlist(lapply(sims[[i]]$betahat.qval,"[[","pi0"))

      res[[i]] = data.frame(Scenario=i,pi0=pi0,qvalue=pi0_qval,mixfdr=pi0_mixfdr, locfdr=pi0_locfdr, fdrtool=pi0_fdrtool,ash.nullbiased=pi0_ash.n,ash.uniform=pi0_ash.u)
    }
    cbbPalette <- c("#56B4E9", "#009E73", "#F0E442", "#0072B2", "#E69F00", "#000000", "#D55E00", "#CC79A7")
    labels = c('mixfdr','qvalue','locfdr','fdrtool','ash (null-biased)','ash (mle)')
    breaks = c("mixfdr","qvalue","locfdr","fdrtool","ash.nullbiased","ash.uniform")

    require(reshape2)
    res.melt = melt(res, id.vars=c("pi0","Scenario"),variable.name="Method")
    res.melt = res.melt[sample(1:nrow(res.melt)),]  
    res.melt$Scenario = as.factor(res.melt$Scenario)
    levels(res.melt$Scenario) = c("Scenario 1a","Scenario 1b","Scenario 2")
    p=ggplot(data=res.melt,aes(pi0,value,colour=Method)) +geom_point(shape=1) +
        facet_grid(. ~ Scenario) +
      geom_abline(colour = "black") +
        xlab("True pi0") +
        ylab("Estimated pi0")
    print(p +scale_y_continuous(limits=c(0,1)) +
          scale_x_continuous(limits=c(0,1)) +
          scale_colour_manual(values=cbbPalette,breaks=breaks,labels=labels) +
          coord_equal(ratio=1))

@@

  png("figures/estpi0_sim1sim2.png",height=160,width=540)
    plot_pi0(list(simres1,simres1a,simres2))
  dev.off()

@@

```{r}
mean_quant=function(x, mult = 1){
      x <- na.omit(x)
      sd <- mult * sqrt(var(x))
      mean <- mean(x)
      data.frame(y = median(x), ymin = quantile(x,0.25) , ymax = quantile(x,0.75))
}

@@

    cbbPalette <- c("#000000","#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
    labels = c('ash (null-biased)','ash (mle)')
    breaks = c("ash.nullbiased","ash.uniform")
    if(ptype=="lfdr"){
      labels = c('mixfdr', labels)
      breaks = c("mixfdr", breaks)
    }

@@

    res.melt = melt(res, id.vars=c("Bayes","Scenario","Measure"),variable.name="Method")
    res.melt$Scenario = as.factor(res.melt$Scenario)
    levels(res.melt$Scenario) = c("Scenario 1a","Scenario 1b","Scenario 2")

    cbbPalette <- c("#E69F00","#000000", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
    labels = c('mixfdr','ash (null-biased)','ash (mle)')
    breaks = c("mixfdr","ash.nullbiased","ash.uniform")

@@

```{r}
png("figures/lfsdr_sim1sim2_blowup.png",height=427,width=720)
  plot_lfsdr(list(simres1,simres1a,simres2),0.1,ymax=0.2,ptype="lfsra")
dev.off()
```

### 2013-11-14 paper/Rcode/NoisyIllustration.rmd
updated figures and text

```{r}
#install q value package
#source("http://bioconductor.org/biocLite.R")
#biocLite("qvalue")
setwd("~/Documents/git/ash/Rcode/")
library("qvalue")
library("lattice") #library for some of the plots

@@

```{r}
p= data.frame(pval=pval,type=c(rep("GOOD",500),rep("POOR",500)))
histogram(~pval|type,p,layout=c(1,2),xlim=c(0,1),breaks=seq(from=0,to=1,length=20),type="count")
```

@@

```{r}
library("ashr")
beta.ash.all = ash(betahat,s)
beta.ash.good = ash(betahat[p$type=="GOOD"],s[p$type=="GOOD"])
plot(beta.ash.good$PosteriorMean,beta.ash.all$PosteriorMean[p$type=="GOOD"])
plot(beta.ash.good$PositiveProb,beta.ash.all$PositiveProb[p$type=="GOOD"])
```

>>>>

```{r}
#install q value package
#source("http://bioconductor.org/biocLite.R")
#biocLite("qvalue")
library("qvalue")
library("lattice") #library for some of the plots

@@

```{r}
p= data.frame(pval=pval,type=c(rep("GOOD",500),rep("POOR",500)))
require(ggplot2)
pdf("figures/good_poor_hist.pdf",height=3,width=6)
ggplot(p, aes(x=pval)) + facet_grid(.~type)  +
    geom_histogram(aes(y=..density..),binwidth=.05,
                   colour="black", fill="white")

  #old version, using trellis
  #histogram(~pval|type,p,layout=c(1,2),xlim=c(0,1),breaks=seq(from=0,to=1,length=20),type="count")
dev.off()
```

@@

```{r}
library("ashr")
library("locfdr")
beta.ash.all = ash(betahat,s,method="fdr")
beta.ash.good = ash(betahat[p$type=="GOOD"],s[p$type=="GOOD"],method="fdr")
beta.ash.all.z = ash(betahat/s,1,method="fdr")
beta.ash.good.z = ash(betahat[p$type=="GOOD"]/s[p$type=="GOOD"],1,method="fdr")
beta.locfdr.all.z = locfdr(betahat/s,nulltype=0,plot=0)
beta.locfdr.good.z = locfdr(betahat[p$type=="GOOD"]/s[p$type=="GOOD"],nulltype=0,plot=0)
res = rbind(data.frame(x=beta.ash.good$lfsr,y=beta.ash.all$lfsr[p$type=="GOOD"],type="ash"), 
            #data.frame(x=beta.ash.good.z$lfsr,y=beta.ash.all.z$lfsr[p$type=="GOOD"],type='ash, z scores'),
            data.frame(x=beta.locfdr.good.z$fdr,y=beta.locfdr.all.z$fdr[p$type=="GOOD"],type='locfdr'), 
            data.frame(x= qq.good$qvalues, y = qq.all$qvalues[p$type=="GOOD"],type="qvalue") )

pdf("figures/good_vs_all.pdf",height=3,width=6.5)
  pp= ggplot(data=res,aes(x,y)) +geom_point(shape=1) +
        facet_grid(. ~ type) +
      geom_abline(colour = "black") +
        xlab("lfsr/lfdr/qvalue (Good data only)") +
        ylab("lfsr/lfdr/qvalue (All data)")

  print(pp +scale_y_continuous(limits=c(0,1)) +
          scale_x_continuous(limits=c(0,1))  +
          coord_equal(ratio=1))

dev.off()
```
